SciPy - some descriptive title here

### 2018-06-28 scipy-1.0/paper.tex
First round of revisions for manuscript PR 32 -- improving the abstract draft based on feedback.

\title {SciPy 1.0 - Fundamental Algorithms for Scientific Computing in Python}

\author[1]{Pauli Virtanen}
\author[2,*]{Ralf Gommers}
\author[3,4]{Tyler Reddy}
\author[5]{Anne Archibald}
\author[6]{Andrew Nelson}
\author[7]{Charles Harris}
\author[8]{CJ Carey}
\author[9]{Denis Laxalde}
\author[10]{Eric Larson}
\author[11]{Eric Moore}
\author[12]{Eric Quintero}
\author[13]{Evgeni Burovski}
\author[14]{Jaime Fernández del Río}
\author[15]{Josef Perktold}
\author[16]{Josh Wilson}
\author[17]{Matthew Brett}
\author[18]{Nikolay Mayorov}
\author[19]{Warren Weckesser}
\author[20]{Matt Haberland}
\author[21]{Scott Sievert}
\author[22]{Yu Feng}
\author[23]{Antonio Horta Ribeiro}

\affil[1]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}
\affil[3]{UC Berkeley Institute for Data Science,
          Berkeley, CA, 94720, USA}
\affil[4]{Los Alamos National Laboratory,
	  Theoretical Division 6,
          Los Alamos, NM, 87545, USA}
\affil[5]{Affiliation, department, city, postcode, country}
\affil[6]{Affiliation, department, city, postcode, country}
\affil[7]{Affiliation, department, city, postcode, country}
\affil[8]{Affiliation, department, city, postcode, country}
\affil[9]{Affiliation, department, city, postcode, country}
\affil[10]{Affiliation, department, city, postcode, country}
\affil[11]{Affiliation, department, city, postcode, country}
\affil[12]{Affiliation, department, city, postcode, country}
\affil[13]{Affiliation, department, city, postcode, country}
\affil[14]{Affiliation, department, city, postcode, country}
\affil[15]{Affiliation, department, city, postcode, country}
\affil[16]{Affiliation, department, city, postcode, country}
\affil[17]{Affiliation, department, city, postcode, country}
\affil[18]{Affiliation, department, city, postcode, country}
\affil[19]{Affiliation, department, city, postcode, country}
\affil[20]{Affiliation, department, city, postcode, country}
\affil[21]{Affiliation, department, city, postcode, country}
\affil[22]{Affiliation, department, city, postcode, country}
\affil[23]{Affiliation, department, city, postcode, country}

@@

\begin{abstract}
TODO. Abstract must be under 200 words and not include subheadings or citations.
\end{abstract}
\begin{document}

>>>>

\title {SciPy - some descriptive title here}

\author[1]{Pauli Virtanen}
\author[2,*]{Ralf Gommers}
\author[3]{TODO}
\affil[1]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}

@@

% NOTE: some usage stats below are from https://libraries.io/pypi/scipy
% as well as github metrics; normally one doesn't put citations directly
% in abstract though (depends on field / journal)
\begin{abstract}
SciPy is an open source scientific computing library for the Python programming language.
SciPy 1.0 was released in late 2017, about 16 years after the original
version 0.1 release. SciPy
has become a \emph{de facto} standard for leveraging scientific algorithms
in the Python programming language, with more than 600
unique code contributors, millions of downloads per year, 161 dependent
packages, and 28700 dependent respositories.
The library includes functionality spanning clustering, Fourier transforms,
integration, interpolation, file I/O, linear algebra, image processing,
orthogonal distance regression, minimization algorithms, signal processing,
sparse matrix handling, computational geometry, and statistics. In this
work, we provide an overview of the capabilities and development practices of the
SciPy library and highlight some recent technical developments.
\end{abstract}
\begin{document}
